### 2022-07-17 paper/akweury/document.tex
update an loss

\documentclass[]{article}
\usepackage{amssymb}
\usepackage[backend=bibtex,style=authoryear,natbib=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)

@@

\usepackage[autostyle=true]{csquotes} % Required to generate language-dependent quotes in the bibliography

\usepackage{tikz}
\usepackage{tikz-network}
\usetikzlibrary{calc,patterns,angles,quotes}
\usepackage{breqn}
\usepackage{bm}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{graphicx}
\usetikzlibrary{fit}
\usetikzlibrary {arrows.meta,graphs,shapes.misc}
\usetikzlibrary {positioning}

\newcommand{\bn}{\textbf{n}}
\newcommand{\tabhead}[1]{\textbf{#1}}

@@

\subsection{Intrinsic image decomposition}
Intrinsic image model was introduced by \cite{intrinsic-image}. It interprets that an image $ I $ can be decomposed as the element-wise product between the reflectance $ R $ of the object and the shading $ S $ produced by the interaction between light and objects.
\[ I =R  \odot S\]
It interprets the observed image into reflectance image and the shading image. As shown in Figure \ref{fig:intrinsic-image}
%% insert a image for decompositions
\begin{figure}[th]
	\centering
	{\includegraphics[width=.18\textwidth]{./Figures/intrinsic_image.png}}
	{\includegraphics[width=.18\textwidth]{./Figures/intrinsic_image_reflectance.png}}
	{\includegraphics[width=.18\textwidth]{./Figures/intrinsic_image_shading.png}}
	{\includegraphics[width=.18\textwidth]{./Figures/intrinsic_image_light.png}}
	{\includegraphics[width=.18\textwidth]{./Figures/intrinsic_image_normal.png}}
	\decoRule	
	\caption{Intrinsic image analysis of the bus object. From left to right, original image, reflectance image, shading image, light image, normal image}
	\label{fig:intrinsic-image}
\end{figure}

@@

\begin{figure}[th]
	\centering
	{\includegraphics[width=.4\textwidth]{./Figures/intrinsic_image_vertex_input.png}}
	{\includegraphics[width=.4\textwidth]{./Figures/intrinsic_image_light_input.png}}
	\decoRule	
	\caption{The light map calculated from vertex map and the light source}
	\label{fig:light-input}
\end{figure}

In order to ease this issue, a light inpainting model has been trained based on the GCNN network. It takes the semi-dense light map as input and predict the fully dense light map.

@@

		\node[text width=3.5cm] at (\vdist*\disttimes,\yschift-1) {Light Net};
\end{tikzpicture}

\caption{Light Net for light inpainting based on GCNN architecture.}
\label{fig:light-net-archi}
\end{figure}

\subsection{Light and image guided normal inference using GCNN}
Based on above implementations, we propose a Triple Gated Convolutional Neural Network (TriGNet) to perform guided normal inference. The structure is shown in Figure \ref{fig:albedo-gated-archi}. As shown in the name, the network is constructed based on three GCNN architectures: Image GCNN, Light GCNN, and Vertex GCNN.

>>>>

\documentclass[border=15pt, multi, tikz]{article}
\usepackage{amssymb}
\usepackage[backend=bibtex,style=authoryear,natbib=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)

@@

\usepackage[autostyle=true]{csquotes} % Required to generate language-dependent quotes in the bibliography
\usepackage{import}
\usepackage{tikz}
\usepackage{tikz-network}
\usetikzlibrary{calc,patterns,angles,quotes}
\usepackage{breqn}
\usepackage{bm}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{graphicx}
\usetikzlibrary{fit}
\usetikzlibrary {arrows.meta,graphs,shapes.misc}
\usetikzlibrary {positioning}
\subimport{./layers/}{init}
\newcommand{\bn}{\textbf{n}}
\newcommand{\tabhead}[1]{\textbf{#1}}

\def\ConvColor{rgb:yellow,5;red,2.5;white,5}
\def\ConvReluColor{rgb:yellow,5;red,5;white,5}
\def\PoolColor{rgb:red,1;black,0.3}
\def\DcnvColor{rgb:blue,5;green,2.5;white,5}
\def\SoftmaxColor{rgb:magenta,5;black,7}
\def\SumColor{rgb:blue,5;green,15}
\def\poolsep{1}

@@

\subsection{Intrinsic image decomposition}
Intrinsic image model was introduced by \cite{intrinsic-image}. It interprets that an image $ I $ can be decomposed as the element-wise product between the reflectance $ R $ of the object and the shading $ S $ produced by the interaction between light and objects.
\[ I =R  \odot S\]
It interprets the observed image into reflectance image and the shading image. As shown in Figure \ref{fig:intrinsic-image}
%% insert a image for decompositions
\begin{figure}[th]
	\centering
	{\includegraphics[width=.18\textwidth]{./Figures/intrinsic_image.png}}
	{\includegraphics[width=.18\textwidth]{./Figures/intrinsic_image_reflectance.png}}
	{\includegraphics[width=.18\textwidth]{./Figures/intrinsic_image_shading.png}}
	{\includegraphics[width=.18\textwidth]{./Figures/intrinsic_image_light.png}}
	{\includegraphics[width=.18\textwidth]{./Figures/intrinsic_image_normal.png}}
	\caption{Intrinsic image analysis of the bus object. From left to right, original image, reflectance image, shading image, light image, normal image}
	\label{fig:intrinsic-image}
\end{figure}

@@

\begin{figure}[th]
	\centering
	{\includegraphics[width=.4\textwidth]{./Figures/intrinsic_image_vertex_input.png}}
	{\includegraphics[width=.4\textwidth]{./Figures/intrinsic_image_light_input.png}}
	\caption{The light map calculated from vertex map and the light source}
	\label{fig:light-input}
\end{figure}

In order to ease this issue, a light inpainting model has been trained based on the GCNN network with the identity architecture but the input and output, which takes the semi-dense light map as input and predict the fully dense light map as output.

@@

		\node[text width=3.5cm] at (\vdist*\disttimes,\yschift-1) {Light Net};
\end{tikzpicture}
\caption{Light Net for light inpainting based on GCNN architecture.}
\label{fig:light-net-archi}
\end{figure}

\subsection{Light and image guided normal inference using GCNN}
Based on above implementations, we propose a Three branches Gated Convolutional Neural Network (TriGNet) to perform guided normal inference. The structure is shown in Figure \ref{fig:albedo-gated-archi}. As shown in the name, the network utilizes the GCNN architecture three times to accomplish the task.

\begin{figure}[th]
	\centering 
	\begin{tikzpicture}
		\tikzstyle{connection}=[ultra thick,every node/.style={sloped,allow upside down},draw=\edgecolor,opacity=0.6]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Draw Layer Blocks
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% conv1_1,conv1_2,%pool1
\pic[shift={(0,0,0)}] at (0,0,0) {RightBandedBox={name=cr1,%
		xlabel={{"64","64"}},zlabel=I,fill=\ConvColor,bandfill=\ConvReluColor,%
		height=40,width={2,2},depth=40}};
\pic[shift={(\poolsep,0,0)}] at (cr1-east) {Box={name=p1,%
		fill=\PoolColor,opacity=0.5,height=30,width=1,depth=30}};
% conv2_1,conv2_2,pool2
\pic[shift={(1,0,0)}] at (p1-east) {RightBandedBox={name=cr2,%
		xlabel={{"64","64"}},zlabel=I/2,fill=\ConvColor,bandfill=\ConvReluColor,%
		height=30,width={3,3},depth=30}};
\pic[shift={(\poolsep,0,0)}] at (cr2-east) {Box={name=p2,%
		fill=\PoolColor,opacity=0.5,height=23,width=1,depth=23}};
% conv3_1,conv3_2,pool3
\pic[shift={(1,0,0)}] at (p2-east) {RightBandedBox={name=cr3,%
		xlabel={{"256","256","256"}},zlabel=I/4,fill=\ConvColor,bandfill=\ConvReluColor,%
		height=23,width={4,4,4},depth=23}};
\pic[shift={(\poolsep,0,0)}] at (cr3-east) {Box={name=p3,%
		fill=\PoolColor,opacity=0.5,height=14,width=1,depth=14}};
% conv4_1,conv4_2,conv4_3,pool4
\pic[shift={(1,0,0)}] at (p3-east) {RightBandedBox={name=cr4,%
		xlabel={{"512","512","512"}},zlabel=I/8,fill=\ConvColor,bandfill=\ConvReluColor,%
		height=14,width={7,7,7},depth=14}};
\pic[shift={(\poolsep,0,0)}] at (cr4-east) {Box={name=p4,%
		fill=\PoolColor,opacity=0.5,height=8,width=1,depth=8}};
% conv5_1,conv5_2,conv5_3,pool5
\pic[shift={(1,0,0)}] at (p4-east) {RightBandedBox={name=cr5,%
		xlabel={{"512","512","512"}},fill=\ConvColor,bandfill=\ConvReluColor,%
		height=8,width={7,7,7},depth=8}};
%% fc8 -> cr8 (score32)
\pic[shift={(0,0,0)}] at (cr5-east) {Box={name=score16,%
		xlabel={{"K","dummy"}},fill=\ConvColor,%
		height=8,width=2,depth=8,zlabel=I/16}};

%% Upsampling Deconv Layer
%% Dcnv16    
\pic[shift={(2.5,0,0)}] at (score16-east) {Box={name=d16,%
		xlabel={{"","dummy"}},fill=\DcnvColor,opacity=0.7,height=40,width=0.5,depth=40}};
%% Dcnv8    
\pic[shift={(.25,0,0)}] at (d16-east) {Box={name=d8,%
		xlabel={{"","dummy"}},fill=\DcnvColor,opacity=0.7,height=40,width=0.5,depth=40}};
%% Dcnv4    
\pic[shift={(.25,0,0)}] at (d8-east) {Box={name=d4,%
		xlabel={{"","dummy"}},fill=\DcnvColor,opacity=0.7,height=40,width=0.5,depth=40}};
%% Dcnv2    
\pic[shift={(.25,0,0)}] at (d4-east) {Box={name=d2,%
		xlabel={{"","dummy"}},fill=,opacity=0.01,height=40,width=0.5,depth=40}};

%% Dcnv envelope    
\pic[shift={(-0.2,0,0)}] at (d16-west) {Box={name=env,caption=concatenation of deconvolved feature maps,%
		xlabel={{"","dummy"}},fill=,opacity=0.2,height=42,width={8},depth=42}};
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\def\skipshift{6.5}
%%Joining with previous streams (fcn-16)
%% score16
\pic[shift={(0,0,3+\skipshift)}] at (cr5-anchor) {Box={name=score8,%
		xlabel={{"K","dummy"}},fill=\ConvColor,height=14,width=2,depth=14,zlabel=I/8}};
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%Joining with previous streams (fcn-8)
%% score8
\pic[shift={(0,0,8+\skipshift)}] at (cr4-east) {Box={name=score4,%
		xlabel={{"K","dummy"}},fill=\ConvColor,height=23,width=2,depth=23,zlabel=I/4}};
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%Joining with previous streams (fcn-4)
%% score4
\pic[shift={(1,0,13+\skipshift)}] at (cr3-east) {Box={name=score2,%
		xlabel={{"K","dummy"}},fill=\ConvColor,height=30,width=2,depth=30,zlabel=I/2}}; 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%Joining with previous streams (fcn-2)
%% score2
\pic[shift={(0.3,0,22+\skipshift)}] at (p2-east) {Box={name=score,%
		xlabel={{"K","dummy"}},fill=\ConvColor,height=40,width=2,depth=40,zlabel=I}};
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Final convolution

\pic[shift={(3,0,0)}] at (d2-east) {Box={name=output,%
		xlabel={{"K","dummy"}},fill=\ConvColor,height=40,width=2,depth=40,zlabel=I}};
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Draw connections
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\draw [connection]  (cr1-east)    -- node {\midarrow} (p1-west);
\draw [connection]  (p1-east)    -- node {\midarrow} (cr2-west);
\draw [connection]  (cr2-east)    -- node {\midarrow} (p2-west);
\draw [connection]  (p2-east)    -- node {\midarrow} (cr3-west);
\draw [connection]  (cr3-east)    -- node {\midarrow} (p3-west);
\draw [connection]  (p3-east)    -- node {\midarrow} (cr4-west);
\draw [connection]  (cr4-east)    -- node {\midarrow} (p4-west);
\draw [connection]  (p4-east)    -- node {\midarrow} (cr5-west);
\draw [connection]  (score16-east)    -- node {\midarrow} (d16-west);
%
\path (cr4-east) -- (p4-west) coordinate[pos=0.4] (after4) ;
\draw (d16-near)++(0,0,-1+\skipshift) coordinate (d16h);
\draw [connection]  (after4)    -- node {\midarrow} ++(0,0,3+\skipshift) -- node {\midarrow} (score8-west);
\draw [connection]  (score8-east) -- node{\midarrow} (d16h) -- node{\midarrow}(d16-near);
%
\path (cr3-east) -- (p3-west) coordinate[pos=0.4] (after3) ;
\draw (d8-near)++(0,0,4+\skipshift) coordinate (d8h);
\draw [connection]  (after3)    -- node {\midarrow} ++(0,0,8+\skipshift) -- node {\midarrow} (score4-west);
\draw [connection]  (score4-east) -- node{\midarrow} (d8h) -- node{\midarrow}(d8-near);
%
\path (cr2-east) -- (p2-west) coordinate[pos=0.4] (after2) ;
\draw (d4-near)++(0,0,9+\skipshift) coordinate (d4h);
\draw [connection]  (after2)    -- node {\midarrow} ++(0,0,13+\skipshift) -- node {\midarrow} (score2-west);
\draw [connection]  (score2-east) -- node{\midarrow} (d4h) -- node{\midarrow}(d4-near);
%
\path (cr1-east) -- (p1-west) coordinate[pos=0.4] (after1) ;
\draw (d2-near)++(0,0,18+\skipshift) coordinate (d2h);
\draw [connection]  (after1)    -- node {\midarrow} ++(0,0,22+\skipshift) -- node {\midarrow} (score-west);
\draw [connection]  (score-east) -- node{\midarrow} (d2h) -- node{\midarrow}(d2-near);

\draw [connection]  (d2-east)    -- node {\midarrow} (output-west);
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\end{tikzpicture}
	\caption{TriGNet Architecture}
	\label{fig:trig-net-archi}
\end{figure}
